**The Heart can Lie: A Preliminary Investigation of the Role of Interoception and Theory of Mind in Deception**

### 2024-06-25 paper/manuscript.Rmd
footnote on title page + move citation in discussion
sorry i cannot knit no more T_T

Additionally to the limitations pertaining to the measure of lying ability, some also concern the measure of the predictor constructs, namely ToM and interoception. While we tried to include a behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure. In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT). While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity have been highlighted in several studies [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart]. Given increasing research efforts invested in the development of novel interoception tasks [@plans2021measuring; @legrand2022heart; @ponzo2021measuring], future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.

>>>>

Additionally to the limitations pertaining to the measure of lying ability, some also concern the measure of the predictor constructs, namely ToM and interoception. While we tried to include a behavioral task as well as a subjective questionnaire for each, it has to be underlined that they are notoriously difficult concepts to measure. In particular, objective interoceptive accuracy was assessed using the Heartbeat Counting Task (HCT). While the HCT used to be considered as a gold standard and remains one of the most commonly used measures [@desmedt2022does], concerns regarding its validity have been increasingly highlighted in several studies as more research efforts are invested into developing novel interoception tasks [@desmedt2018heartbeat; @desmedt2022does; @brener2016towards; @legrand2022heart; @plans2021measuring; @ponzo2021measuring]. Future works should further examine the relationship between interoception and lying ability using measures with better psychometric properties.
